%کلمات کلیدی انگلیسی
\latinkeywords{Dimention reduction, Random projection, Stable distribution, Large scale data}
%چکیده انگلیسی

\en-abstract{
The porblems of dimention reduction has become more important when large scale data emerged and we faced the serious problems
in storing and processing those data in memory.
Random projectino is a dimention reduction method that can be applied on
large scale big data and also on the data flows.
This method is based on multipliyng initial data matrix with a projection matrix that reduces dimention, 
however, the statistical information in original data remains with required and satisfactory accuracy.
Data which the number of the parameters of the model are more than the samples is called "large scale data".
Random projection for dimention reduction of large scale data have many advantages over other methods
including: hight speed in processing, limited memory requirements, being applicable on data flows and being applicable when
number of parameters are more than samples.
In this thesis, the method of dimention reduction has been explained and compared with other methods.
Also, application of this method on the data with non-normal stable distribution is evaluated and compared with other methods.
The comparision of different methods resulted that random projection have acceptable efficinecy with large scale data in many conditions and
it is an optimum way thanks to computational cost.
Although, in most conditions it is, required to do this method multiple times to ensure satisfing results.
}
%%%%%%%%%%%%%%%%%%%%% کدهای زیر را تغییر ندهید.

\newpage
\thispagestyle{empty}
\begin{latin}
\section*{\LARGE\centering Abstract}

\een-abstract

\vspace*{.5cm}
{\large\textbf{Key Words:}}\par
\vspace*{.5cm}
\elatinkeywords
\end{latin}
