---
title: "Random projection to dimention reduction of large scale data "
author: "Siamak Dehbod"
date: "January 18, 2019"
output:
  beamer_presentation:
    theme: "Antibes"
    keep_tex: yes
    colortheme: "dolphin"
    fonttheme: "structurebold"
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# In the morning

## Getting up

- Turn off alarm
- Get out of bed

### Using third level

## Breakfast

- Eat eggs
- Drink coffee

# In the evening

## Dinner

- Eat spaghetti
- Drink wine

---

```{r, carss, fig.cap="A scatterplot.", echo=FALSE}
plot(cars)
```

## Going to sleep

- Get in bed
- Count sheep


## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

