---
title: "Thesis Reports"
author: "S.Dehbod"
date: "January 8, 2019"
output:
  pdf_document: 
    keep_tex: yes
  html_notebook: default
---

# For $\alpha$ = 2, p(reduced dimention) = 2

## Tabel_A2D2
```{r , include=FALSE}
rm(list = ls(all.names = TRUE))
library(kableExtra)
load('SimData_A2D2_1ig.RData')
```

```{r , echo=FALSE}
tabel1 <- data.frame(Dataset = character(length(d)), ARI_d = numeric(length(d)), ARI_p = numeric(length(d)), C_e = numeric(length(d)), stringsAsFactors = FALSE)
for(dIndex in 1:length(d)){
td <- d[[dIndex]]
tabel1[dIndex, ] <- data.frame(Dataset = td$name,
                                ARI_d  = mean(td$ARIreport[,1]), 
                                ARI_p  = mean(td$ARIreport[,2]), 
                                C_e    = -round(mean(td$ARIreport[,3])),
                              stringsAsFactors = FALSE)
}
kable(tabel1, "latex", booktabs = T) %>%
kable_styling(latex_options = "striped")
```

## Histograms
```{r, out.width='1\\linewidth', fig.align='center', echo=FALSE}
for(dIndex in names(d)){
hist(d[[dIndex]]$ARIreport[,2], breaks = 50, main = bquote(paste(.(d[[dIndex]]$name),' ',ARI[d])), xlab = 'ARI')
}
```

# For $\alpha$ = 2, p(reduced dimention) = 3

## Tabel
```{r , include=FALSE}
rm(list = ls(all.names = TRUE))
library(kableExtra)
load('SimData_A2D3_1im.RData')
```

```{r, echo=FALSE}
tabel1 <- data.frame(Dataset = character(length(d)), ARI_d = numeric(length(d)), ARI_p = numeric(length(d)), C_e = numeric(length(d)), stringsAsFactors = FALSE)
for(dIndex in 1:length(d)){
td <- d[[dIndex]]
tabel1[dIndex, ] <- data.frame(Dataset = td$name,
                                ARI_d  = mean(td$ARIreport[,1]), 
                                ARI_p  = mean(td$ARIreport[,2]), 
                                C_e    = -round(mean(td$ARIreport[,3])),
                              stringsAsFactors = FALSE)
}
kable(tabel1, "latex", booktabs = T) %>%
kable_styling(latex_options = "striped")
```

## Histograms
```{r, out.width='1\\linewidth', fig.align='center', echo=FALSE}
for(dIndex in names(d)){
hist(d[[dIndex]]$ARIreport[,2], breaks = 50, main = bquote(paste(.(d[[dIndex]]$name),' ',ARI[d])), xlab = 'ARI')
}
```

# For $\alpha$ = 1, p(reduced dimention) = 2

## Tabel
```{r , include=FALSE}
rm(list = ls(all.names = TRUE))
library(kableExtra)
load('SimData_A1D2_1io.RData')
```

```{r, echo=FALSE}
tabel1 <- data.frame(Dataset = character(length(d)), ARI_d = numeric(length(d)), ARI_p = numeric(length(d)), C_e = numeric(length(d)), stringsAsFactors = FALSE)
for(dIndex in 1:length(d)){
td <- d[[dIndex]]
tabel1[dIndex, ] <- data.frame(Dataset = td$name,
                                ARI_d  = mean(td$ARIreport[,1]), 
                                ARI_p  = mean(td$ARIreport[,2]), 
                                C_e    = -round(mean(td$ARIreport[,3])),
                              stringsAsFactors = FALSE)
}
kable(tabel1, "latex", booktabs = T) %>%
kable_styling(latex_options = "striped")
```

## Histograms
```{r, out.width='1\\linewidth', fig.align='center', echo=FALSE}
for(dIndex in names(d)){
hist(d[[dIndex]]$ARIreport[,2], breaks = 50, main = bquote(paste(.(d[[dIndex]]$name),' ',ARI[d])), xlab = 'ARI')
}
```

# For $\alpha$ = 1, p(reduced dimention) = 3

## Tabel
```{r , include=FALSE}
rm(list = ls(all.names = TRUE))
library(kableExtra)
load('SimData_A1D3_1in.RData')
```

```{r, echo=FALSE}
tabel1 <- data.frame(Dataset = character(length(d)), ARI_d = numeric(length(d)), ARI_p = numeric(length(d)), C_e = numeric(length(d)), stringsAsFactors = FALSE)
for(dIndex in 1:length(d)){
td <- d[[dIndex]]
tabel1[dIndex, ] <- data.frame(Dataset = td$name,
                                ARI_d  = mean(td$ARIreport[,1]), 
                                ARI_p  = mean(td$ARIreport[,2]), 
                                C_e    = -round(mean(td$ARIreport[,3])),
                              stringsAsFactors = FALSE)
}
kable(tabel1, "latex", booktabs = T) %>%
kable_styling(latex_options = "striped")
```

## Histograms
```{r, out.width='1\\linewidth', fig.align='center', echo=FALSE}
for(dIndex in names(d)){
hist(d[[dIndex]]$ARIreport[,2], breaks = 50, main = bquote(paste(.(d[[dIndex]]$name),' ',ARI[d])), xlab = 'ARI')
}
```


# For $s$ = 2, p(reduced dimention) = 2

## Tabel
```{r , include=FALSE}
rm(list = ls(all.names = TRUE))
library(kableExtra)
load('SimData_S2D2_1jK.RData')
```

```{r, echo=FALSE}
tabel1 <- data.frame(Dataset = character(length(d)), ARI_d = numeric(length(d)), ARI_p = numeric(length(d)), C_e = numeric(length(d)), stringsAsFactors = FALSE)
for(dIndex in 1:length(d)){
td <- d[[dIndex]]
tabel1[dIndex, ] <- data.frame(Dataset = td$name,
                                ARI_d  = mean(td$ARIreport[,1]), 
                                ARI_p  = mean(td$ARIreport[,2]), 
                                C_e    = -round(mean(td$ARIreport[,3])),
                              stringsAsFactors = FALSE)
}
kable(tabel1, "latex", booktabs = T) %>%
kable_styling(latex_options = "striped")
```

## Histograms
```{r, out.width='1\\linewidth', fig.align='center', echo=FALSE}
for(dIndex in names(d)){
hist(d[[dIndex]]$ARIreport[,2], breaks = 50, main = bquote(paste(.(d[[dIndex]]$name),' ',ARI[d])), xlab = 'ARI')
}
```

# For $s$ = 2, p(reduced dimention) = 2

## Tabel
```{r , include=FALSE}
rm(list = ls(all.names = TRUE))
library(kableExtra)
load('SimData_S2D3_1jR.RData')
```

```{r, echo=FALSE}
tabel1 <- data.frame(Dataset = character(length(d)), ARI_d = numeric(length(d)), ARI_p = numeric(length(d)), C_e = numeric(length(d)), stringsAsFactors = FALSE)
for(dIndex in 1:length(d)){
td <- d[[dIndex]]
tabel1[dIndex, ] <- data.frame(Dataset = td$name,
                                ARI_d  = mean(td$ARIreport[,1]), 
                                ARI_p  = mean(td$ARIreport[,2]), 
                                C_e    = -round(mean(td$ARIreport[,3])),
                              stringsAsFactors = FALSE)
}
kable(tabel1, "latex", booktabs = T) %>%
kable_styling(latex_options = "striped")
```

## Histograms
```{r, out.width='1\\linewidth', fig.align='center', echo=FALSE}
for(dIndex in names(d)){
hist(d[[dIndex]]$ARIreport[,2], breaks = 50, main = bquote(paste(.(d[[dIndex]]$name),' ',ARI[d])), xlab = 'ARI')
}
```

# For ARI vs alpha, p(reduced dimention) = 2

## Data
```{r , include=FALSE}
rm(list = ls(all.names = TRUE))
library(kableExtra)
load('SimData_ARIvsAlphaD2_1jM.RData')
```

## Plot
```{r, out.width='1\\linewidth', fig.align='center', echo=FALSE}
for(dIndex in names(d)){
plot(d[[dIndex]]$ARIvsAlpha[,1], -d[[dIndex]]$ARIvsAlpha[,6],
     type = 'o',
     main = bquote(.(d[[dIndex]]$name)~C[e]~' vs.'~alpha), xlab = bquote(alpha), ylab=bquote(C[e]))
}
```

# For ARI vs alpha, p(reduced dimention) = 3

## Data
```{r , include=FALSE}
rm(list = ls(all.names = TRUE))
library(kableExtra)
load('SimData_ARIvsAlphaD3_1jP.RData')
```

## Plot
```{r, out.width='1\\linewidth', fig.align='center', echo=FALSE}
for(dIndex in names(d)){
plot(d[[dIndex]]$ARIvsAlpha[,1], -d[[dIndex]]$ARIvsAlpha[,6],
     type = 'o',
     main = bquote(.(d[[dIndex]]$name)~C[e]~' vs.'~alpha), xlab = bquote(alpha), ylab=bquote(C[e]))
}
```

# For ARI vs s, p(reduced dimention) = 2

## Data
```{r , include=FALSE}
rm(list = ls(all.names = TRUE))
library(kableExtra)
load('SimData_ARIvsSD2_1jN.RData')
```

## Plot
```{r, out.width='1\\linewidth', fig.align='center', echo=FALSE}
for(dIndex in names(d)){
plot(d[[dIndex]]$ARIvsAlpha[,1], -d[[dIndex]]$ARIvsAlpha[,6],
     type = 'o',
     main = bquote(.(d[[dIndex]]$name)~C[e]~' vs.'~s), xlab = bquote(s), ylab=bquote(C[e]))
}
```

# For ARI vs s, p(reduced dimention) = 3

## Data
```{r , include=FALSE}
rm(list = ls(all.names = TRUE))
library(kableExtra)
load('SimData_ARIvsSD3_1jQ.RData')
```

## Plot
```{r, out.width='1\\linewidth', fig.align='center', echo=FALSE}
for(dIndex in names(d)){
plot(d[[dIndex]]$ARIvsAlpha[,1], -d[[dIndex]]$ARIvsAlpha[,6],
     type = 'o',
     main = bquote(.(d[[dIndex]]$name)~C[e]~' vs.'~s), xlab = bquote(s), ylab=bquote(C[e]))
}
```
